Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-17 graph_wine_exp1_distr.tex
remerging Mykel's comments

\begin{tikzpicture}
  \begin{groupplot}[group style={group size=1 by 2}]%,xmin=0,ymin=0,height=4cm,width=5cm,no markers]
  \nextgroupplot[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			ylabel=K,
			colorbar right,
    every colorbar/.append style={height=
        2*\pgfkeysvalueof{/pgfplots/parent axis height}+
        \pgfkeysvalueof{/pgfplots/group/vertical sep}},
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.5},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

>>>>

\begin{tikzpicture}
  \begin{groupplot}[group style={group size=1 by 2}]%,xmin=0,ymin=0,height=4cm,width=5cm,no markers]
  \nextgroupplot[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			ylabel=K,
			colorbar right,
    every colorbar/.append style={height=
        2*\pgfkeysvalueof{/pgfplots/parent axis height}+
        \pgfkeysvalueof{/pgfplots/group/vertical sep}},
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.51},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]
